---
title: "Solve Puzzles FastR"
author: Ryan Hardiman
format: 
  revealjs:
    footer: "Solving Puzzles FastR"
    transition: slide
    transition-speed: fast
    theme: blood
    css: styles.css
editor: visual
---

```{r setup}
library(tidyverse)
library(memoise)
library(knitr)
# library(kableExtra)
library(glue)
```


```{r}
#| echo: false

#Function to draw grids, includes a basic character replacement to facilitate
#highlights etc.
mk_grid <- function(grid_string, .left = "{", .right = "}", class = "grid_highlight") {
  header <- r"(<div class="grid">
<pre class="gridpre">)"
  footer <- r"(</pre>
</div>)"
  
  highlight_header <- glue::glue('<span class="{class}">')
  highligh_footer <- glue::glue("</span>")
  
  grid_string <- grid_string |>
    stringr::str_replace_all(pattern = stringr::str_escape(.left),
                             replacement = highlight_header) |>
    stringr::str_replace_all(pattern = stringr::str_escape(.right),
                             replacement = highligh_footer)
  
  cat(paste0(header, grid_string, footer, collapse = "\n"))
}
```

## Overview

-   AoC questions \[Spoilers\]

-   Participation

-   🔧 Tools and Techniques

-   📖 Further Reading

-   ❓ Questions

## Behind the Puzzles: The Fine Print

Advent of Code is a registered trademark in the United States.
The design elements, language, styles, and concept of Advent of Code are all the sole property of Advent of Code and may not be replicated or used by any other person or entity without express written consent of Advent of Code.
Copyright 2015-2024 Advent of Code.
All rights reserved.

You may link to or reference puzzles from Advent of Code in discussions, classes, source code, printed material, etc., even in commercial contexts.
You will nod if you acknowledge to reading the text.
Advent of Code does not claim ownership or copyright over your solution implementation.

## Now That We're All Legal...

:::::::: r-stack
::: {.fragment .fade-in-then-out}
*...You may link to or reference puzzles from Advent of Code in discussions, classes, source code, printed material, etc., even in commercial contexts. [You will nod if you have read this text]{style="color:green;"}. Advent of Code does not claim ownership or copyright over your solution implementation.*
:::

:::::: r-stack
::::: {.fragment .fade-in style="text-align: bottom-left;"}
Tip #1: Always read the fine print.

:::: {.fragment .fade-in style="text-align: bottom-left;"}
Missed details often lead to missed points.

::: {.fragment .fade-in style="text-align: bottom-left;"}
And sometimes...
to solving the wrong problem.
:::
::::
:::::
::::::
::::::::

## Grids! Get used to them.

Say you are given this grid:

::::::::::::: r-stack
:::: {.fragment .fade-in-then-out}
::: {style="text-align: center; font-size: 1.5em; font-family: monospace; font-weight: bold;"}
```{r results="asis"}
mk_grid(r"(.|...\.... 
|.-.\..... 
.....|-... 
........|. 
.......... 
.........\ 
..../.\\.. 
.-.-/..|.. 
.|....-|.\ 
..//.|....)")
```
:::
::::

:::: {.fragment .fade-in-then-out}
::: {style="text-align: center; font-size: 1.5em; font-family: monospace; font-weight: bold;"}

```{r results="asis"}
mk_grid(r"({.|}...\.... 
|.-.\..... 
.....|-... 
........|. 
.......... 
.........\ 
..../.\\.. 
.-.-/..|.. 
.|....-|.\ 
..//.|....)")
```
:::
::::

:::: {.fragment .fade-in-then-out}
::: {style="text-align: center; font-size: 1.5em; font-family: monospace; font-weight: bold;"}
```{r results="asis"}
mk_grid(r"({.|}...\.... 
|{.}-.\..... 
.{.}...|-... 
.{.}......|. 
.{.}........ 
.{.}.......\ 
.{.}../.\\.. 
.{-}.-/..|.. 
.|....-|.\ 
..//.|....)")
```
:::
::::


:::: {.fragment .fade-in-then-out}
::: {style="text-align: center; font-size: 1.5em; font-family: monospace; font-weight: bold;"}
```{r results="asis"}
mk_grid(r"({.|}...\.... 
|{.}-.\..... 
.{.}...|-... 
.{.}......|. 
.{.}........ 
.{.}.......\ 
.{.}../.\\.. 
{.-.-/}..|.. 
.|....-|.\ 
..//.|....)")
```
:::
::::


:::: {.fragment .fade-in-then-out}
::: {style="text-align: center; font-size: 1.5em; font-family: monospace; font-weight: bold;"}
```{r results="asis"}
mk_grid(r"({.|}...\.... 
|{.}-.\..... 
.{.}...|-... 
.{.}......|. 
.{.}........ 
.{.}.......\ 
.{.}..{/}.\\.. 
{.-.-/}..|.. 
.|....-|.\ 
..//.|....)")
```
:::
::::

:::: {.fragment .fade-in-then-out}
::: {style="text-align: center; font-size: 1.5em; font-family: monospace; font-weight: bold;"}
```{r results="asis"}
mk_grid(r"({.|}...\.... 
|{.}-.\..... 
.{.}...|-... 
.{.}......|. 
.{.}........ 
.{.}.......\ 
.{.}..{/.\}\.. 
{.-.-/}..|.. 
.|....-|.\ 
..//.|....)")
```
:::
::::

:::: {.fragment .fade-in-then-out}
::: {style="text-align: center; font-size: 1.5em; font-family: monospace; font-weight: bold;"}
```{r results="asis"}
mk_grid(r"({.|...\}.... 
|{.}-.\{.}.... 
.{.}...{|-...} 
.{.}...{..}.|. 
.{.}...{..}... 
.{.}...{..}..\ 
.{.}..{/.\\}.. 
{.-.-/..|}.. 
.{|....-|}.\ 
.{.}//.{|}.{.}..)")
```
:::
::::
:::::::::::::

## Trees - 2024 day 14

-   100x100 grid.
-   Lots of dots moving about.
-   Each dot moves a consistent, unique amount each second.
-   Dots "teleport" when they reach the border.

Q: At what time does a tree exist?

## Trees (Sub-Questions)

Lets first ask some easier questions.

::::: r-stack
:::: {.fragment .fade-in style="text-align: bottom"}
🌳 What does a tree look like

::: {.fragment .fade-in style="text-align: bottom"}
🕒 How can we know when it happens
:::
::::
:::::

## Memoise Memorise Mesmarise

## Practice Makes Puzzling Easier

The more puzzles you solve, the sharper your skills become

With over 500 Advent of Code challenges already available (250 days, two parts each), there's no shortage of material to learn from.

Set yourself a challenge: how far can you get in just one month?

https://adventofcode.com/
